Demographic Shifts in Toronto's Homeless Population: Evaluating and Reassessing City Solutions

### 2024-09-23 paper/paper.qmd
changed repo structure

---
title: "My title"
author: 
  - Junbo Li
thanks: "Code and data are available at: https://github.com/Junbo345/Homeless."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Demographic Shifts in Toronto's Homeless Population: Evaluating and Reassessing City Solutions"
author: 
  - Junbo Li
thanks: "Code and data are available at: https://github.com/Junbo345/Homeless."
date: today
date-format: long
abstract: "Reducing homeless population in city of Toronto is an ongoing task. While the reduce method by the government stays the same, the demographic of the population varys in the past six years. In our paper, we analysis the demographic change of homless population and show that the traditional solution is no longer effective. We will then present new solutions of better adapt the on-going shift of demographics."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
